---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rmdprotectr

<!-- badges: start -->
<!-- badges: end -->

The goal of `rmdprotectr` is to password protect Rmarkdown HTML documents.

> Very simple password protection to static pages or whole websites with no server configuration required: you can use Dropbox, Amazon S3 or any generic hosting service to host a private, password protected site.

## Installation

You can install the development version of rmdprotectr from [GitHub](https://github.com/favstats/rmdprotectr) with:

```{r, eval = F}
remotes::install_github("rmdprotectr")
```

## How to Use


```{r example, eval = F}
library(rmdprotectr)

## provide a path to your .Rmd and it will be rendered in the correct folder
protect_rmd("test.Rmd", pw = "somefancypw")

```

You are set! Push to private GitHub repo and activate GitHub pages or whatever hosting service you prefer!

### Things to consider 

- If your hosting service offers directory listing, a visitor can bypass the protection.
- there's no protection against brute force attack. Pick a very long and hard to guess password.
- Pasting the link directly to someone will bypass the login

Credit to [matteobrusa](https://github.com/matteobrusa/Password-protection-for-static-pages) and [scottishstoater](https://github.com/scottishstoater/protected-github-pages) for their initial findings and implementation.
